Results

### 2023-03-17 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added direction of results

``` {r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  df.descr,
  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
  booktabs = TRUE,
  escape = FALSE,
  placement = "H")
```

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$
As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).<!--JZ: Auch hier gern die Richtung des Effekts mit hinschreiben (dass Corrugator und Utility beide mit höheren SVs zusammenhängen, ist ja eher unerwartet-->
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).

>>>>

``` {r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  df.descr,
  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
  escape = FALSE,
  placement = "H",
  landscape = TRUE)
```

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$
As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).
